### 2017-03-03 Hhh/Hhh.tex
Own final read through

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner \htotautau final state.

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), 2jet-1tag 
(at least two jets, exactly one of which is b-tagged), 2jet-2tag (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
\end{center}
\caption[Reconstruced di-tau invariant mass and di-jet invariant mass in
the 2jet-2tag category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the 2jet-2tag category of the \mutau
channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
The signal peaks at around $125\,\GeV$ in both variables.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

@@

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
under consideration.

@@

As illustrated in figure \ref{fig:kinfitvsmjj}a the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs boson mass in signal events, when 
compared with the simple four-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. It is also insightful to make such a comparison
for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between four-body mass and
kinematic fit mass for \ttbar events is shown in figure 
\ref{fig:kinfitvsmjj}b. From this figure we can see that the mass distribution for
background events is less affected by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to $250\,\GeV$.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category the total
yield after the initial event selection, before subdividing into categories, as
estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low-\mT~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

The shape of the \Wjets distribution is taken from the simulation. To 
increase the number of events for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is relaxed from the medium to the loose 
working point for the purposes of shape estimation.
\subsection{QCD multijet}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Here, di-tau candidates
of the same sign, which otherwise pass the signal region selection, are used. 
The contributions from other backgrounds
in this same-sign (SS) region are subtracted from the number of data events obtained.
As the contributions from opposite-sign (OS) and same-sign QCD are
not exactly the same an OS/SS ratio is applied to the same-sign region data yield with other backgrounds subtracted.
The OS/SS ratio is measured using data with 
the electron or muon isolation requirements inverted.

@@

\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region. The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.

@@

The second term in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section \ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
ensures that the process yields can never become negative, and therefore unphysical, in the fit. 
%For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
%uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
%an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
%yields do not become negative. 
Shape uncertainties are accounted for using a vertical template morphing
technique \cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter is added to the likelihood model with a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template is allowed to vary within its statistical uncertainty, independent of the other bins. %These
%variations are controlled by log-normal constraints in the likelihood function.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \Htohhtobbtautau process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.

The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.

\begin{table}[htp]
\begin{center}
\caption{Couplings in the type-II 2HDM.}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up-type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down-type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}

The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
and \AtoZh analyses, overlaid on the \xsbr.
The exclusion contours have some interesting features, most of which can be explained by the couplings
in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
centre of the graphs in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
as the coupling of the \PHiggslight to pairs of b-quarks or tau leptons is proportional 
to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non-exclusion
at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
to become visible in the \xsbr structure of the \Htohh interpretation, but
the analysis is not yet sensitive enough to actually observe it.
%Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
%interpretation, these are a result of the complex \Htohh branching ratio.

@@

The combined interpretation of both analyses in this model is presented figure 
\ref{fig:HhhAZhMSSM2HDM}b.
%The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
%very sensitive in this model. 
By combining the two analyses a slightly larger amount
of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
described for the figure \ref{fig:HhhAndAZhlowtanb}b are also visible in this figure. In a small region of phase
space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with $125\pm3\,\GeV$.
This region is therefore excluded, as indicated by the red band.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
\subfloat[low-\tanb~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in a type-II 2HDM and in the low-\tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
(b) in the low-\tanb~MSSM scenario. The shaded blue area bounded by
the solid black line indicates the observed excluded region at 95\% \ac{CL}.
The dashed black line indicates the expected exclusion, with the grey bands showing
the $\pm 1\sigma$ and $\pm2\sigma$ probability intervals on the expected exclusion \cite{CMS-HIG-14-034}. The area
bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$
 and is therefore excluded.}
\label{fig:HhhAZhMSSM2HDM}
\end{center}
\end{figure}

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner $\PHiggslight(125) \rightarrow \Pgt\Pgt$ final state.

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
\end{center}
\caption[Reconstructed di-tau invariant mass and di-jet invariant mass in
the \mbox{2jet-2tag} category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the \mbox{2jet-2tag} category of the \mutau
channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
The signal peaks at around $125\,\GeV$ in both variables.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

@@

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
P(\text{demote}) &= 1 - \text{SF} \text{  for SF < 1 }  \notag \\
P(\text{promote}) &= \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
under consideration.

@@

As illustrated in figure \ref{fig:kinfitvsmjj}a the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs boson mass in signal events, when 
compared with the simple four-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. It is also insightful to make such a comparison
for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between four-body mass and
kinematic fit mass for \ttbar events is shown in figure 
\ref{fig:kinfitvsmjj}b. This figure shows that the mass distribution for
background events is less affected by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to $250\,\GeV$.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category the total
yield after the initial event selection, before subdividing into categories, as
estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

The shape of the \Wjets distribution is taken from the simulation. To 
increase the number of events for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is relaxed from the medium to the loose 
working point for the purpose of shape estimation.
\subsection{QCD multijet}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Here, di-tau candidates
of the same sign, which otherwise pass the signal region selection, are used. 
The contributions from other backgrounds
in this same-sign (SS) region are subtracted from the number of data events obtained.
As the contributions from opposite-sign (OS) and same-sign QCD are
not exactly the same an OS/SS ratio is applied to the same-sign region data yield with other backgrounds subtracted.
The OS/SS ratio is measured using data with 
the electron or muon isolation requirements inverted.

@@

\item \Wjets: As the \Wjets yield is estimated from a high-\mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region. The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.

@@

The second term in equation \ref{eqn:hhh_likelihood}, $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section~\ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainty. Normalisation uncertainties are applied with log-normal constraints, which
ensures that the process yields can never become negative, and therefore unphysical, in the fit. 
%For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
%uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
%an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
%yields do not become negative. 
Shape uncertainties are accounted for using a vertical template morphing
technique~\cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter is added to the likelihood model with a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template is allowed to vary within its statistical uncertainty, independent of the other bins. %These
%variations are controlled by log-normal constraints in the likelihood function.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \mbox{\Htohhtobbtautau} process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.
The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.

The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
and \AtoZh analyses, overlaid on the \xsbr.
The exclusion contours have some interesting features, most of which can be explained by the couplings
in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
\begin{table}[htp]
\begin{center}
\caption{Couplings in the type-II 2HDM.}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up-type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down-type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}
which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
centre of the graphs in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
as the coupling of the \PHiggslight to pairs of b-quarks or tau leptons is proportional 
to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non-exclusion
at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
to become visible in the \xsbr structure of the \Htohh interpretation, but
the analysis is not yet sensitive enough to actually observe it.
%Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
%interpretation, these are a result of the complex \Htohh branching ratio.

@@

The combined interpretation of both analyses in this model is presented in figure 
\ref{fig:HhhAZhMSSM2HDM}b.
%The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
%very sensitive in this model. 
By combining the two analyses a slightly larger amount
of the \mA-\tanb~plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
described for figure \ref{fig:HhhAndAZhlowtanb}b are also visible in this figure. In a small region of phase
space, at low \mA~and low~\tanb, this scenario predicts a light Higgs boson mass that is not compatible with $125\pm3\,\GeV$.
This region is therefore excluded, as indicated by the red band.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[type-II 2HDM]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_012.pdf}}
\subfloat[low-\tanb~MSSM scenario]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_011.pdf}}
\caption[Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in a type-II 2HDM and in the low-\tanb~MSSM scenario.]{Combination of the \AtoZhtolltautau and \Htohhtobbtautau searches
interpreted in (a) a type-II \ac{2HDM} assuming $m_{\PHiggs} = m_{\PHiggsps} = m_{\PHiggs^{+}} = 300\,\GeV$ and 
(b) in the low-\tanb~MSSM scenario. The blue shaded area bounded by
the solid black line indicates the observed excluded region at 95\% \ac{CL}.
The dashed black line indicates the expected exclusion, with the grey bands showing
the $\pm 1\sigma$ and $\pm2\sigma$ probability intervals on the expected exclusion \cite{CMS-HIG-14-034}. The area
bounded by the red line is the region of phase space where \mh~$\neq 125 \pm 3\,\GeV$
 and is therefore excluded.}
\label{fig:HhhAZhMSSM2HDM}
\end{center}
\end{figure}
